#SeattleCrime
#Jose M Hernandez
#October 15, 2015

```{r, echo=F, warning=F, message=F, include=F}
library(leaflet)
library(maps)
library(rgdal)
library(dplyr)
library(ggplot2)
library(rgeos)
library(maptools)
library(RgoogleMaps)
library(ggmap)
library(jsonlite)
library(curl)
```

#Loading the data from Seattle Open Data (Socrata)

Use curl and jsonlite and downlod as a Json file format limit to the most recent 2,000 incidents 
```{r, warning=F, message=F,}
crime <- fromJSON("https://data.seattle.gov/resource/pu5n-trf4.json?event_clearance_group=ASSAULTS&$limit=2000")

schools <- fromJSON("https://data.seattle.gov/resource/ywms-iep2.json")

crime$latitude<-as.numeric(crime$latitude)
crime$longitude<-as.numeric(crime$longitude)
schools$shape$latitude<-as.numeric(schools$shape$latitude)
schools$shape$longitude<-as.numeric(schools$shape$longitude)
```

##Static version if you're into that ;) 

Locate Seattle using this magical geocode function use open street maps and plot crime points. 

```{r,warning=F, message=F}
CenterOfMap <- geocode("Seattle,WA")

sea_town <- get_map(c(lon=CenterOfMap$lon, lat=CenterOfMap$lat),zoom = 12, source = "osm")
sea_town <- ggmap(sea_town)
sea_town <- sea_town + theme(axis.text.x = element_blank(),
                             axis.text.y = element_blank(),
                             axis.ticks = element_blank())
sea_town
```
Add data 
```{r, warning=F, message=F}
sea_town <- sea_town +
            geom_point( data=crime, aes(x=longitude, y=latitude), 
                        color="red",alpha=0.3,na.rm = T)

sea_town <- sea_town + geom_point( data=schools, aes(x=shape$longitude, y=shape$latitude),
                                   color="blue",shape=18, size=4,alpha=.7,na.rm = T)
sea_town
```

All good, but this maps violent crime at all times, let's only look at crime that happens between 7am and 3pm

```{r, warning=F, message=F}
str(crime$at_scene_time)
crime$time <- substr(crime$at_scene_time, 12,13)
crime$time <-as.numeric(crime$time)
crime_day <-subset(crime, time>=07 & time<=15)
```

I know that theres a more efficient way using the time stamp and as.Date() subsets.

```{r, warning=F, message=F}
sea_town <- sea_town + geom_point( data=crime_day, aes(x=longitude, y=latitude),
                                   color="purple",alpha=0.5, size=3, na.rm = T)
sea_town
```

###Let's plot an inteactive map using leaflet 

```{r,warning=F, message=F,fig.width=10, fig.height=6}
sea_crime <-leaflet() %>%
            addProviderTiles("CartoDB.Positron") %>%
            addCircles(data = crime_day, lng = ~longitude, 
             lat = ~latitude, weight = 2, radius = 50, color = "#ca0020",
             popup = ~initial_type_description, fillOpacity = 0.5) %>%
  
            addCircles(data = schools, lng = ~shape$longitude, lat = ~shape$latitude, 
             weight = 3, radius = 100, color = "#7b3294",
             popup = ~name) %>%
            addLegend("bottomright", colors= c("#ca0020","#7b3294"), 
            labels=c("Assault","School"), title="School Time Crime")


sea_crime
```

###The End.  
